
\section{Mentoring}

\denseouterlist{

\entrymid[\textbullet]
{Mr Giovanni Benetti (Università di Padova)}{2025\textendash Current}
{Master’s student. Supervising project on the impact of waveform systematics in golden dark siren cosmology, with emphasis on mitigating systematic biases in Hubble parameter estimation. Manuscript in preparation.}

\entrymid[\textbullet]
{Ms Akshita Mittal (Gran Sasso Science Institute, Italy)}{2024\textendash Current}
{PhD student (initially mentored as an undergraduate). Leading project on parameter estimation biases in eccentric compact binary mergers, focusing on spurious support for extremal spins in GW231123. Manuscript in preparation.}

\entrymid[\textbullet]
{Ms Shiksha Pandey (Penn State University)}{2024}
{Undergraduate research assistant. Co-supervised project assessing the role of LIGO-India in multi-messenger astronomy for next-generation detectors. Resulted in publication: \href{https://inspirehep.net/literature/2849126}{\textit{Astrophys. J. Lett.} 985 (2025) L17}.}

\entrymid[\textbullet]
{Mr Sayantan Ghosh (IIT Bombay)}{2023\textendash 2024}
{PhD student. Developed coherence tests to distinguish noise transients from intermediate-mass black hole binary signals by assessing posterior consistency across detectors. Resulted in publication: \href{https://doi.org/10.1103/PhysRevD.109.064015}{\textit{Phys. Rev. D 109, 064015 (2024)}}}

\entrymid[\textbullet]
{Ms Kritti Sharma (IIT Bombay)}{2022\textendash 2023}
{Undergraduate student. Developed a transfer learning framework to detect mass-asymmetric black hole binaries in Advanced LIGO data. Resulted in publication: \href{https://doi.org/10.1103/PhysRevD.108.124061}{\textit{Phys. Rev. D} 108 124061 (2023)}}

\entrymid[\textbullet]
{Mr Sagar Gupta (IIT Bombay)}{2022\textendash 2023}
{Undergraduate student. Implemented a chirp-mass–based classifier for glitch identification in gravitational-wave data, improving transient search data-quality vetoes.}}
